The Right Way to Search Evolving Graphs

### 2016-03-04 paper.tex
fix figure caption

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.58]{time.pdf}
  \caption{Experimental run time and memory use of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $1.0\times 10^5$ active nodes and $10$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including only the causal edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.58]{time.pdf}
  \caption{Experimental run time and memory use of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $1.0\times 10^5$ active nodes and $10$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including only the static edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
